Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-19 paper.tex
A sentence

Benchmark code and data are available in our supplement~\cite{supplement}.
The results shown below were obtained on a MacBook Pro with an Apple~M2 Pro processor and \SI{32}{GB} of RAM.
The results are an average of \textcolor{red}{N} (TODO) runs per benchmark.

>>>>

Benchmark code and data are available in our supplement~\cite{supplement}.
The results shown below were obtained on a MacBook Pro with an Apple~M2 Pro processor and \SI{32}{GB} of RAM, averaging over \textcolor{red}{N} (TODO) runs per benchmark.
